Formulating experimental feeds

### 2025-12-17 docs-working/05_formulating_feeds.qmd
Moving data files

ingreds <- file.path(input_feed_profile_path, "all_ingredients.xlsx") %>% 
  read_excel(sheet = "all_ingredients") %>% 
  mutate(ingredient = as.factor(ingredient))

>>>>

ingreds <- file.path(bigdata_path, "all_ingredients.xlsx") %>% 
  read_excel(sheet = "all_ingredients") %>% 
  mutate(ingredient = as.factor(ingredient))
